APOGEE CATALOG OF 10,000+ M DWARFS MEASURED WITH DATA-DRIVEN MODELS

### 2018-08-05 paper/draft.tex
add makefile

\subsection{Test Sample \label{subsec:test_selection}} 
Out of the total APOGEE DR14 catalog of 277,371 sources, we selected 254,478 sources which were in the cross match of Gaia DR2 (\citealt{Brown:2018}) and applied Gaia color-magnitude cuts of $1<BP-RP<6$ and $7.5<M_G<20$, yielding a sample of 14,827 sources. From there we applied the following selection procedure to identify a sample of single, main-sequence M stars. Although our catalog reports the temperatures, metallicities, and spectral types for XXX sources out of 14,000 with $\chi^2<200,000$, the sources we deem ``safe'', with minimal contamination from reddened K dwarfs, pre-main sequence stars, and binaries, are selected by the following criteria (see Figure \ref{fig:cmd_selection}):

>>>>

\subsection{Test Sample \label{subsec:test_selection}} 
Out of the total APOGEE DR14 catalog of 258,475 sources, we selected 254,478 sources which were in the cross match of Gaia DR2 (\citealt{Brown:2018}) and applied Gaia color-magnitude cuts of $1<BP-RP<6$ and $7.5<M_G<20$, yielding a sample of 14,827 sources. From there we applied the following selection procedure to identify a sample of single, main-sequence M stars. Although our catalog reports the temperatures, metallicities, and spectral types for XXX sources out of 14,000 with $\chi^2<200,000$, the sources we deem ``safe'', with minimal contamination from reddened K dwarfs, pre-main sequence stars, and binaries, are selected by the following criteria (see Figure \ref{fig:cmd_selection}):
